Manuscript

### 2014-10-01 inst/simulation/manuscript.Rmd
..

```{r table-1a}
x <- ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
y <- unique(meanPopulationSizes)
join(x, y)
```

```{r table-1b}
x <- ddply(populationSizes2000, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
y <- unique(meanPopulationSizes2000)
join(x, y)
```

@@

@@

>>>>

```{r figure-3-init-10days}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=2000)
populationSizes10days <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes10days)

meanPopulationSizes10days <- ddply(populationSizes10days, .(scenario, modelName), function(x) {
  data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario)
})
logPopulationSizes10days <- populationSizes10days
logPopulationSizes10days$Observed <- log10(logPopulationSizes10days$Observed + 1)
logPopulationSizes10days$Estimated <- log10(logPopulationSizes10days$Estimated + 1)
logMeanPopulationSizes10days <- ddply(populationSizes10days, .(scenario, modelName), function(x) {
  data.frame(True=mean(log10(x$Observed+1)), Estimated=mean(log10(x$Estimated+1)), Scenario=x$scenario)
})
```

```{r figure-3d}
p <- ggplot(populationSizes10days, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) +
  stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") +
  geom_point(data=meanPopulationSizes10days, aes(True, Estimated, colour=modelName), size=2, shape=15) +
  facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3d.png", width=8, height=4)
```

```{r table-1abc}
prettyModelName <- function(x) {
  lookup <- data.frame(x=c("SmoothModel-nbinomial-matern-ar1", "SmoothModel-nbinomial-ar1", "FMPModel") , y=c("ST", "S", "I"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, full=F, file) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x) {
    y <- lm(Estimated~Observed, x)
    data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
  })
  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  y$EstDev <- y$Estimated / y$True
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- substr(z$Scenario, 1, 1)
  if (full) return(z)

  z <- z[,c("Model","Scenario","Slope","EstDev","R2")]
  z$EstDev <- round(z$EstDev, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

dir <- normalizePath(context$figuresDirectory)
getPopulationSizesTable(populationSizes, meanPopulationSizes, file=file.path(dir, "table-1a.csv"))
getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, file=file.path(dir, "table-1b.csv"))
getPopulationSizesTable(populationSizes10days, meanPopulationSizes10days, file=file.path(dir, "table-1c.csv"))
```

@@

```{r figure-4c}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=2000)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1])

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4c.png", width=4, height=4)
```

@@

```{r figure-5c}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5c.png", width=4, height=2)
```
